Commutative Character Sheaves

### 2015-11-13 followup.tex
Fixing typos, moving sections around

\subsection{Commutative character sheaves on commutative groups}\label{ssec:comcom}

Suppose now that $G$ is commutative.
Recall \cite{cunningham-roe:13a}*{Def. 1.1} that a character sheaf on $G$ is a triple $(\gcs{L}, \mu, \phi)$,
where $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, 
$\mu : \bm^* \gcs{L} \to \LxL$ is an isomorphism
of sheaves on $\bG \times \bG$, 
and $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on $\bG$;
the triple $(\gcs{L}, \mu, \phi)$ must also satisfy compatibility conditions specified in \emph{loc. cite}.
The category of character sheaves on $G$ is denoted by $\CS(G)$.

Let $\cs{L}$ be a character sheaf on $G$.  Since $m = m \circ \theta$ in the commutative case,
there is a canonical isomorphism $\xi : m^* \cs{L} \to \theta^* m^* \cs{L}$.
There is also an isomorphism $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$
given on stalks by the canonical map $\gcs{L}_{g} \otimes \gcs{L}_{h} \to \gcs{L}_{h} \otimes \gcs{L}_{g}$.

@@

\subsection{Commutative character sheaves on non-commutative groups}\label{ssec:noncom}

We now drop the assumption that $G$ is commutative, and assume only that it is smooth.
The category $\CS(G)$ still makes sense in this context, defined as in \cite{cunningham-roe:13a}*{Def. 1.1}.
In order to distinguish the resulting objects from
the character sheaves of Lusztig, we will refer to the former as \emph{linear character sheaves}
(to evoke the one-dimensional character sheaves of \cite{Kamgarpour})
and again write $\CS(G)$ for the resulting category, with morphisms defined as in \emph{loc. cite}.

The first step in this process is to rule out character sheaves as above.
The following proposition will be proven in Section \ref{ssec:proofs}.
\begin{proposition} \label{prop:Gder_triv}
Suppose $G$ is a smooth group scheme and $\cs{L} \in \CS(G)$ is a linear character sheaf on $G$.
Then the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $\cs{L} \cong q^*(\cs{L}\ab)$ for some
character sheaf $\cs{L}\ab$ on $G\ab$.
\end{proposition}

\iffalse
\begin{definition}
A linear character sheaf $\cs{L}$ on a smooth group scheme $G$ is \emph{commutative} if
\[
\cs{L} \cong q^* \cs{L}\ab
\]
for a commutative character sheaf $\cs{L}\ab$ on $G\ab$.  As in the commutative case,
we write $\CCS(G)$ for the full subcategory of $\CS(G)$ consisting of commutative character sheaves.
\end{definition}
\fi

\iffalse
Note that we may also pull back the map $\xi\ab : m\ab^* \cs{L}\ab \to \theta\ab^*(m\ab^* \cs{L})$ from Definition \ref{def:CCScom}.
The following proposition will be proven in Section \ref{sec:descent}.

\begin{proposition} \label{prop:Gdiagram}
A linear character sheaf $(\cs{L}, \mu)$ on a smooth group scheme $G$ is commutative if and only if
\begin{enumerate}
\item $\cs{L} \cong q^* \cs{L}\ab$ for some character sheaf $\cs{L}\ab$ on $G\ab$,
\item the following diagram of Weil sheaves on $G \times G$ commutes.
  \[
  \begin{tikzcd}[row sep=30]
   m^*\cs{L} \arrow{d}[swap]{(q\times q)^*\xi\ab} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L})
  \end{tikzcd}
  \]
\end{enumerate}
\end{proposition}
\fi

\section{Eliminating Invisible Character Sheaves}\label{sec:defect}

@@

\section{Descent to the Abelianization} \label{sec:descent}

In this section we use descent along the abelianization $q : G \to G\ab$ to prove Propositions~1.2 and 1.4, and Theorem~\ref{thm:Gab}.
This approach requires introducing equivariant linear character sheaves, as defined in Section~[].

@@

Let $G$ be as above.
Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
Let $a : H \times G\to G$ be a group action compatible with the group structure on $G$ and write $p : H\times G \to G$ for projection. 
Consider the morphisms
\[
\begin{tikzcd}
H \times H \times G 
\arrow[shift left=4]{r}{b_1, b_2, b_3} 
\arrow{r}{}
\arrow[shift right=4]{r}{} 
& H \times G 
\arrow[shift left=2]{r}{a}
\arrow[shift right=2]{r}[swap]{p}
 & G 
\end{tikzcd}
\]
defined by $b_1(h_1,h_2,g) = (n(h_1,h_2),g)$,  $b_2(h_1,h_2,g) = (h_1,a(h_2,g))$ and $b_3(h_1,h_2,g) = (h_2,g)$.
Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
Define $s : G\to H\times G$ by $s(g) = (1,g)$.
An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
\[
\nu : a^*\cs{L} \to p^*\cs{L}
\] 
of Weil local systems on $H\times G$ such that 
\begin{equation}\label{E1}
s^*(\nu) = \id_{\cs{L}}
\end{equation}
and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
\begin{equation}\label{E2}
\begin{tikzcd}
\ &  \arrow{dl}{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
b_1^* a^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L}, & 
\end{tikzcd}
\end{equation}
In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
\iffalse
On stalks, this condition is ...
\[
\begin{tikzcd}
\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
\end{tikzcd}
\]
\fi
Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
\begin{equation}\label{E3}
\begin{tikzcd}
\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
\end{tikzcd}
\end{equation}
commutes.
This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.

@@

An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense. 
Consider the following morphisms: $c_0 : H\times G \times G\to H\times G \times H \times G$ defined by $c_0(h,g_1,g_2)\ceq(h,g_1,h,g_2)$;
$c_1 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$;  $c_2 : H \times G\times G \to H\times G$ defined by $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$; and $c_3 : H \times G\times G \to G\times G$ defined by $c_3(h, g_1, g_2) = (g_1, g_2)$. 
Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
\begin{equation}\label{ECS1}
\begin{tikzcd}
\ & \arrow{dl}{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} &&& c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{dr}{p_i\circ c_1 = a\circ p_i\circ c_0} &&& \arrow{dl}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3} c_3^*(\cs{L}\boxtimes \cs{L}) \\
 & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & 
\end{tikzcd}
\end{equation}
\iffalse
On stalks, this condition is
\[
\begin{tikzcd}
\arrow{d}[swap]{\mu_{(h\cdot g_1, h\cdot g_2)}} \cs{L}_{(h\cdot g_1)(h\cdot g_2)} & \arrow[equal]{l}  \cs{L}_{h\cdot(g_1 g_2)} \arrow{r}{\nu_{(h, g_2 g_2)}} & \cs{L}_{g_1 g_2} \arrow[equal]{r} & \cs{L}_{g_1 g_2} \arrow{d}{\mu_{(g_1,g_2)}} \\
\cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow[equal]{r} & \cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow{r}{\nu_{(h,g_1)}\otimes \nu_{(h,g_2)}} & \cs{L}_{g_1}\otimes \cs{L}_{g_2} & \arrow[equal]{l} \cs{L}_{g_1} \otimes \cs{L}_{g_2},
\end{tikzcd}
\]
for all $(h,g_1,g_2)\in H\times G\times G$.
\fi

A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves.
%so
%\begin{equation}\label{CS4}
%\begin{tikzcd}
%\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
%\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
%\end{tikzcd}
%\end{equation}
%commutes; see also \cite{cunningham-roe:13a}, CS.4].
%
Let $\CS_H(G)$ be the category of $H$-equivariant linear character sheaves on $G$.

@@

\begin{proof} 
Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(m^*\cs{L}, m_2^*(\mu))$, where $m_2 : G\times G\times G\times G\to G\times G$ is defined by $m_2(x_1,y_1,x_2,y_2) = (m(x_1,x_2), m(y_1,y_2)$;
this can be seen by following the argument of \cite{cunningham-roe:13a}].
Set $\cs{L}_2\ceq m^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
The linear character sheaf $(\cs{L}_2,\mu_2)$ comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ where $a_2 : H\times H\times G\times G\to G\times G$ is given by $a_2(h_1,g_1,h_2,g_2) = (a(h_1,g_1), a(h_2,g_2)$ and $p_2 : H\times H\times G\times G\to G\times G$ is given by $p_2(h_1,g_1,h_2,g_2)= ( g_1,g_2)$. 
The  isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
Likewise $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu_2} a_2^*(m^*\cs{L}) \arrow{r}{a_2^*(\mu)} & a_2^*(\cs{L}\boxtimes\cs{L})  \arrow{r} & (a^*\cs{L})\boxtimes (a^*\cs{L}) \arrow{d}{\nu\boxtimes\nu} \\
p_2^*(m^*\cs{L}) \arrow{r}{p_2^*(\mu)} & p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r} & (p^*\cs{L})\boxtimes (p^*\cs{L}) 
\end{tikzcd}
\]
Since this diagram commutes, $(\cs{L}\boxtimes \cs{L},\mu\boxtimes \mu,\nu\boxtimes\nu)$ is also an $H\times H$-equivariant linear character sheaf on $G\times G$.
The appropriate version of \eqref{E3} also commutes, so $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism of equivariant linear character sheaves.
The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.
\end{proof}

@@

Now suppose $q : G \to G_0$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
\[
\begin{tikzcd}
H\times G
 \arrow[shift left=2]{r}{a}
  \arrow[shift right=2,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
G_0
\end{tikzcd}
\]
Let $\cs{L}_0$ be a linear character sheaf on $G_0$.
Consider the functor
\[
q^* : \CS(G_0) \to \CS(G)
\]
given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$; see \cite{cunningham-roe:13a}*{}.
%To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
This linear character sheaf $(\cs{L},\mu)\ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$ on $G$ comes equipped with the canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of canonical isomorphisms.
\[
\begin{tikzcd}
a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{rrr}{\nu} & & &  \arrow[equal]{d} p^*\cs{L} \\
a^* ( q^*\cs{L}_0) \arrow{r} 
& (q\circ a)^* \cs{L}_0 \arrow[equal]{r} 
& (q\circ p)^*\cs{L}_0 \arrow{r} 
& p^* q^*\cs{L}_0
\end{tikzcd}
\]
Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(G_0)$, 
then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, arguing as in \cite{cunningham-roe:13a} so $\alpha$ is a morphism in $\CS(G)$.
%\todo{I find myself having to make many references to \cite{cunningham-roe:13a}] and promising that the results there adapt to the noncommutative group case. It makes me uneasy, but the alternative is to actually repeat the proofs here, with the weaker hypothesis on $G$, which would be ugly. I'm just agonizing out loud, I guess.} 
These simple observations define the comparison functor
\[
q_H^* : \CS(G_0) \to CS_H(G)
\]
and show that the functor $q^* : \CS(G_0) \to \CS(G)$ factors according to the following commuting diagram of functors
\[
\begin{tikzcd}
\CS(G) &\arrow{l}[swap]{q^*} 
\CS(G_0) \arrow{dl}{q_H^*}\\
\arrow{u}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\]
The definition of $q_H^* : \CS(G_0)\to \CS_H(G)$ will be revisited in the proof of the following result.

>>>>

When $G$ is commutative, a \emph{character sheaf} on $G$ is a triple $(\gcs{L}, \mu, \phi)$,
where $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, 
$\mu : \bm^* \gcs{L} \to \LxL$ is an isomorphism
of sheaves on $\bG \times \bG$, 
and $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on $\bG$;
the triple $(\gcs{L}, \mu, \phi)$ is required to satisfy certain conditions \cite{cunningham-roe:13a}*{Def. 1.1}.
Write $\CS(G)$ for the category of character sheaves on $G$.

Even when $G$ is not commutative, the category $\CS(G)$, defined as in \cite{cunningham-roe:13a}*{Def. 1.1},
still makes sense.  In order to distinguish the resulting objects from
the character sheaves of Lusztig, we will refer to the former as \emph{linear character sheaves}
(to evoke the one-dimensional character sheaves of \cite{Kamgarpour}).

\section{Commutative character sheaves on commutative groups}\label{sec:comcom}

We consider first the case that $G$ is commutative, which will be used for general smooth $G$.
Let $\cs{L}$ be a character sheaf on $G$.  Since $m = m \circ \theta$ in this case,
there is a canonical isomorphism $\xi : m^* \cs{L} \to \theta^* m^* \cs{L}$.
There is also an isomorphism $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$
given on stalks by the canonical map $\gcs{L}_{g} \otimes \gcs{L}_{h} \to \gcs{L}_{h} \otimes \gcs{L}_{g}$.

@@

\subsection{Eliminating Invisible Character Sheaves}\label{ssec:defect}

In this section we show that trace of Frobenius is an isomorphism for commutative character sheaves on a
smooth commutative group scheme $G$.  We begin by reinterpreting Definition \ref{def:CCScom} in terms of
cocycles.

@@

\section{Commutative character sheaves on non-commutative groups}\label{sec:noncom}

We now consider the case of a smooth group scheme without the commutativity assumption.  We start
by relating character sheaves on $G$ to character sheaves on its abelianization.

\subsection{Definition}\label{ssec:noncomdef}

In order to get character sheaves that correspond to characters in $G(k)^*$, we must discard those
character sheaves whose restriction to the derived subgroup is nontrivial.
The following proposition will be proven in Section \ref{ssec:proofs}.
\begin{proposition} \label{prop:Gder_triv}
Suppose $G$ is a smooth group scheme and $\cs{L} \in \CS(G)$ is a linear character sheaf on $G$.
Then the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $\cs{L} \cong q^*(\cs{L}\ab)$ for some
character sheaf $\cs{L}\ab$ on $G\ab$.
\end{proposition}

\todo{Should remark that it reduces to the other definition in the commutative case}

%\section{Descent to the Abelianization} \label{sec:descent}

%In this section we use descent along the abelianization $q : G \to G\ab$ to prove Propositions~1.2 and 1.4, and Theorem~\ref{thm:Gab}.
%This approach requires introducing equivariant linear character sheaves, as defined in Section~[].

@@

Let $G$ be a smooth group scheme over $k$, as above.
Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
Let $a : H \times G\to G$ be a group action compatible with the group structure on $G$ and write $p : H\times G \to G$ for projection. 
Consider the morphisms
\[
\begin{tikzcd}
H \times H \times G 
\arrow[shift left=4]{r}{b_1, b_2, b_3} 
\arrow{r}{}
\arrow[shift right=4]{r}{} 
& H \times G 
\arrow[shift left=2]{r}{a}
\arrow[shift right=2]{r}[swap]{p}
 & G 
\end{tikzcd}
\]
defined by $b_1(h_1,h_2,g) = (n(h_1,h_2),g)$,  $b_2(h_1,h_2,g) = (h_1,a(h_2,g))$ and $b_3(h_1,h_2,g) = (h_2,g)$.
Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
Define $s : G\to H\times G$ by $s(g) = (1,g)$.
An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
\[
\nu : a^*\cs{L} \to p^*\cs{L}
\] 
of Weil local systems on $H\times G$ such that 
\begin{equation}\label{E1}
s^*(\nu) = \id_{\cs{L}}
\end{equation}
and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
\begin{equation}\label{E2}
\begin{tikzcd}
\ &  \arrow{dl}{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
b_1^* a^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L}, & 
\end{tikzcd}
\end{equation}
In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
\iffalse
On stalks, this condition is ...
\[
\begin{tikzcd}
\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
\end{tikzcd}
\]
\fi
Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
\begin{equation}\label{E3}
\begin{tikzcd}
\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
\end{tikzcd}
\end{equation}
commutes.
This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.

@@

An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense \todo{of...}. 
Consider the following morphisms: $c_0 : H\times G \times G\to H\times G \times H \times G$ defined by $c_0(h,g_1,g_2)\ceq(h,g_1,h,g_2)$;
$c_1 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$;  $c_2 : H \times G\times G \to H\times G$ defined by $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$; and $c_3 : H \times G\times G \to G\times G$ defined by $c_3(h, g_1, g_2) = (g_1, g_2)$. 
Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
\begin{equation}\label{ECS1}
\begin{tikzcd}
\ & \arrow{dl}{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} &&& c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{dr}{p_i\circ c_1 = a\circ p_i\circ c_0} &&& \arrow{dl}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3} c_3^*(\cs{L}\boxtimes \cs{L}) \\
 & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & 
\end{tikzcd}
\end{equation}
\iffalse
On stalks, this condition is
\[
\begin{tikzcd}
\arrow{d}[swap]{\mu_{(h\cdot g_1, h\cdot g_2)}} \cs{L}_{(h\cdot g_1)(h\cdot g_2)} & \arrow[equal]{l}  \cs{L}_{h\cdot(g_1 g_2)} \arrow{r}{\nu_{(h, g_2 g_2)}} & \cs{L}_{g_1 g_2} \arrow[equal]{r} & \cs{L}_{g_1 g_2} \arrow{d}{\mu_{(g_1,g_2)}} \\
\cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow[equal]{r} & \cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow{r}{\nu_{(h,g_1)}\otimes \nu_{(h,g_2)}} & \cs{L}_{g_1}\otimes \cs{L}_{g_2} & \arrow[equal]{l} \cs{L}_{g_1} \otimes \cs{L}_{g_2},
\end{tikzcd}
\]
for all $(h,g_1,g_2)\in H\times G\times G$.
\fi

A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ \todo{How does this $\nu$ give you the $\nu$ of Section 3.2?} which is also a morphism of linear character sheaves.
%so
%\begin{equation}\label{CS4}
%\begin{tikzcd}
%\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
%\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
%\end{tikzcd}
%\end{equation}
%commutes; see also \cite{cunningham-roe:13a}, CS.4].
%
Let $\CS_H(G)$ be the category of $H$-equivariant linear character sheaves on $G$.

@@

\begin{proof} 
Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(m^*\cs{L}, m_2^*(\mu))$, where $m_2 : G\times G\times G\times G\to G\times G$ is defined by $m_2(x_1,y_1,x_2,y_2) = (m(x_1,x_2), m(y_1,y_2)$;
this can be seen by following the argument of \cite{cunningham-roe:13a} \todo{which part of [2]?}.
Set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
The linear character sheaf $(\cs{L}_2,\mu_2)$ comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ where $a_2 : H\times H\times G\times G\to G\times G$ is given by $a_2(h_1,g_1,h_2,g_2) = (a(h_1,g_1), a(h_2,g_2)$ and $p_2 : H\times H\times G\times G\to G\times G$ is given by $p_2(h_1,g_1,h_2,g_2)= ( g_1,g_2)$. 
The  isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,\nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
Likewise $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu_2} a_2^*(m^*\cs{L}) \arrow{r}{a_2^*(\mu)} & a_2^*(\cs{L}\boxtimes\cs{L})  \arrow{r} & (a^*\cs{L})\boxtimes (a^*\cs{L}) \arrow{d}{\nu\boxtimes\nu} \\
p_2^*(m^*\cs{L}) \arrow{r}{p_2^*(\mu)} & p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r} & (p^*\cs{L})\boxtimes (p^*\cs{L}) 
\end{tikzcd}
\]
Since this diagram commutes, $(\cs{L}\boxtimes \cs{L},\mu\boxtimes \mu,\nu\boxtimes\nu)$ is also an $H\times H$-equivariant linear character sheaf on $G\times G$.
The appropriate version of \eqref{E3} also commutes, so $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism of equivariant linear character sheaves.
The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.
\end{proof}

@@

Now suppose $q : G \to G_0$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
\[
\begin{tikzcd}
H\times G
 \arrow[shift left=2]{r}{a}
  \arrow[shift right=2,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
G_0.
\end{tikzcd}
\]
Let $\cs{L}_0$ be a linear character sheaf on $G_0$.
Consider the functor
\[
q^* : \CS(G_0) \to \CS(G)
\]
given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$; see \cite{cunningham-roe:13a}*{}.
%To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
This linear character sheaf $(\cs{L},\mu)\ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$ on $G$ comes equipped with the canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of canonical isomorphisms.
\[
\begin{tikzcd}
a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{rrr}{\nu} & & &  \arrow[equal]{d} p^*\cs{L} \\
a^* ( q^*\cs{L}_0) \arrow{r} 
& (q\circ a)^* \cs{L}_0 \arrow[equal]{r} 
& (q\circ p)^*\cs{L}_0 \arrow{r} 
& p^* (q^*\cs{L}_0)
\end{tikzcd}
\]
Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(G_0)$, 
then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, arguing as in \cite{cunningham-roe:13a} so $\alpha$ is a morphism in $\CS(G)$.
%\todo{I find myself having to make many references to \cite{cunningham-roe:13a}] and promising that the results there adapt to the noncommutative group case. It makes me uneasy, but the alternative is to actually repeat the proofs here, with the weaker hypothesis on $G$, which would be ugly. I'm just agonizing out loud, I guess.} 
These simple observations define the comparison functor
\[
q_H^* : \CS(G_0) \to CS_H(G)
\]
and show that the functor $q^* : \CS(G_0) \to \CS(G)$ factors according to the following commuting diagram of functors
\[
\begin{tikzcd}
\CS(G) &\arrow{l}[swap]{q^*} 
\CS(G_0) \arrow{dl}{q_H^*}\\
\arrow{u}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\]
The definition of $q_H^* : \CS(G_0)\to \CS_H(G)$ will be revisited in the proof of the following result.
